Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-05-30 documents/TriangleScenarioArXiv/ts.tex
Inflation technique -> Inflation Technique

    Ultimately, this work accomplishes two important tasks. First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation technique specifically for quantum causal inference problems. The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure --- a task that no other existing techniques have succeeded at. In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure. Consequently, this work strongly indicates that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory. Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations. In conclusion \ref{r:1} has been positively solved through the derivation of the inequalities found in \cref{sec:found_inequalities}.

@@

    In the context of the Inflation technique, a variable symmetry $\Phi\br{\mscenario'}$ over an inflated marginal scenario $\mscenario'$ does not always correspond to a variable symmetry under deflation $\Phi\br{\mscenario}$. In order to derive deflated inequalities that are symmetric under an exchange of parties, it is required that $\Phi\br{\mscenario'} \sim \Phi\br{\mscenario}$ are equivalent up to copy-index.

>>>>

    Ultimately, this work accomplishes two important tasks. First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation Technique specifically for quantum causal inference problems. The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure --- a task that no other existing techniques have succeeded at. In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation Technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure. Consequently, this work strongly indicates that the Inflation Technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory. Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations. In conclusion \ref{r:1} has been positively solved through the derivation of the inequalities found in \cref{sec:found_inequalities}.

@@

    In the context of the Inflation Technique, a variable symmetry $\Phi\br{\mscenario'}$ over an inflated marginal scenario $\mscenario'$ does not always correspond to a variable symmetry under deflation $\Phi\br{\mscenario}$. In order to derive deflated inequalities that are symmetric under an exchange of parties, it is required that $\Phi\br{\mscenario'} \sim \Phi\br{\mscenario}$ are equivalent up to copy-index.
